---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LogiReg

<!-- badges: start -->
<!-- badges: end -->

The goal of LogiReg is to perform logistic regression. 

## Installation

You can install the development version of LogiReg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AU-R-Data-Science/Final_Project_6_ProkashNoahShangjia")
```

## Example

This is a basic example which shows you how to use the package 

```{r example, warning=FALSE}
library(LogiReg)

# basic example code of how the logistic regression works with this package

## Importing the dataframe. We are using mtcars ecardio dataset from canvas for example. 
st <- read.csv("student.csv")
y_train <- ifelse(st[,24]=="yes", 1, 0)
x <- st[,c(32, 33, 34, 8, 17, 16, 30)]
x_train <- data.matrix(x, rownames.force = NA)
```


## logistic_regression function will provide predicted values of y

```{r, warning=FALSE}
y_pred <- logistic_regression(x_train=x_train, y_train=y_train, 
                              num_epochs = 100, lr=0.1, cutoff=0.35)
y_pred
```

## logistic_regression_trainer function will provide the estimated beta value

```{r, warning=FALSE}
beta_est <- logistic_regression_trainer(x_train = x_train, y_train = y_train,num_epochs = 100, lr=0.1)
beta_est
```

## logistic_reg_predict_dataset funcion predict y given estimated beta values from logistic_regression_trainer function

```{r}
y_pred_con <- logistic_reg_predict_dataset(x_train, beta_est)
y_pred_con
```


## ConI function is the confident interval by using Bootstrap

```{r, warning=FALSE}
beta_ci <- ConI(0.05, x_train, y_train, B=20)
beta_ci
```


## logireg_Plot funtion is use to plot the fitted logistic curve to the actual values

```{r, warning=FALSE}
plot <- logireg_Plot(x_train, y_train)
```


## confusion_matrix function perform confusion matrix

```{r, warning=FALSE}
con_mat <- confusion_matrix(y_pred, y_train, cutoff_value = 0.35)
```


## Make_table function provide accuracy over cutoff values

```{r, warning=FALSE}
acc_cut <- Make_table(y_pred_con, y_train)
acc_cut
```


























